National Longitudinal Evidence for Growth in Subjective Well-being from Spiritual Beliefs

### 2021-04-05 Supplement_And_Analysis.Rmd
updated supplement

```{r read_data, cache=TRUE}
# custom function for my machine to read data. you'll need to read data to your machine. tweak function in the `funs.R` script for your machine
d<-data_read_mymachine()

@@

# Unique participants

@@

```{r latextable, cache=TRUE}
library(modelsummary)
ts<-d_3 %>%
  dplyr::select(Age, 
                NZdep,
                Education,
                Employed,
                Ethnic_Categories,
                Male,
                Has_Partner, 
                Political_Conservativism,
                Urban, 
                Beliefs, 
                LIFESAT,
                PWI,
                Wave)
modelsummary::datasummary_balance( ~ Wave, data=ts, dinm=FALSE, output = 'table.tex')
# https://github.com/IndrajeetPatil/ggstatsplot
# https://www.datanovia.com/en/lessons/compute-summary-statistics-in-r/

@@

```{r demographic table, cache=TRUE}
# must remove Furniture package before running table 1
demographic_table(d_3)
#demographic_table_latex() not wurking  d
```

>>>>

```{r read_data, cache=TRUE}
# custom function for my machine to read data. you'll need to read data to your machine. tweak function in the `funs.R` script for your machine
d <- data_read_mymachine()

@@

Unique participants

@@

```{r latextable, cache=TRUE}
library(modelsummary)
ts<-d_3 %>%
  dplyr::select(Age, 
                NZdep,
                Education,
                Employed,
                Ethnic_Categories,
                Male,
                Has_Partner, 
                Political_Conservativism,
                Urban, 
                Beliefs, 
                LIFESAT,
                PWI,
                Wave)
modelsummary::datasummary_balance( ~ Wave, data=ts, dinm=FALSE, output = 'table.tex')
modelsummary::datasummary_balance( ~ Wave, data=ts, dinm=FALSE)
# https://github.com/IndrajeetPatil/ggstatsplot
# https://www.datanovia.com/en/lessons/compute-summary-statistics-in-r/

@@

```{r demographic table, cache=TRUE}
# must remove this table is is for the manuscript
demographic_table(d_3)
#demographic_table_latex() not wurking  d
```
